Presentation Title

### 2018-04-04 paper/s1-intro.tex
Polish

Another way to improve transaction rate is to use traditional Byzantine consensus algorithms such as PBFT~\cite{castro1999practical} in a permissioned ledger such as Hyperledger Fabric~\cite{cachin2016architecture}.
In essence, such systems contain a fixed set of nodes (sometimes called validating peer) that run a Byzantine consensus algorithm to decide on new blocks.
They can achieve much higher transaction rates, e.g., 10,000 TPS if the number of validating peer is under 16 for PBFT~\cite[Section 5.2]{miller2016honey}.
However, these systems do not scale, e.g., the transaction rate drops to under 5000 TPS when the number of validating peer is 64~\cite[Section 5.2]{miller2016honey}.
Moreover, the validating peers are predetermined which makes the system unsuitable for the open internet.

@@

\textbf{Research question.\quad}
Thus far, there are no systems that achieve horizontal scalability in the general case,
which leads to the goal of this work.
Hence the research question which we wish to answer is as follows.
\begin{displayquote}
    \emph{How can we design a horizontally scalable blockchain consensus protocol?}
    \end{displayquote}
Concretely, a blockchain consensus protocol should be application neutral.
For example, PoW is application neutral because transaction semantics does not affect it,
i.e. it can be applied in different applications such as cryptocurrency (Bitcoin) and domain name system (Namecoin~\cite{namecoin}).
Further, we are interested in horizontal scalability in the general case as it enables ubiquitous use.
That is, adding more nodes to the network should result in higher transaction throughput.

>>>>

Another way to improve transaction rate is to use traditional Byzantine consensus algorithms such as PBFT~\cite{castro1999practical} in a permissioned ledger such as Hyperledger Fabric~\cite{cachin2016architecture}.
In essence, such systems contain a fixed set of nodes, called validating peers, that run a Byzantine consensus algorithm to decide on new blocks.
They can achieve much higher transaction rates, e.g., 10,000 TPS if the number of validating peers is under 16 for PBFT~\cite[Section 5.2]{miller2016honey}.
However, these systems do not scale, e.g., the transaction rate drops to under 5000 TPS when the number of validating peer is 64~\cite[Section 5.2]{miller2016honey}.
Moreover, the validating peers are predetermined which makes the system unsuitable for the open internet.

@@

\textbf{Research question.\quad}
Thus far, there are no systems that achieve horizontal scalability in the general case,
which leads to the goal of this work.
Hence, the research question which we wish to answer is as follows.
\begin{displayquote}
    \emph{How can we design a horizontally scalable blockchain consensus protocol?}
    \end{displayquote}
Concretely, a blockchain consensus protocol should be application neutral.
For example, PoW is application neutral because transaction semantics does not affect it,
i.e. it can be applied in different applications such as cryptocurrency (Bitcoin) and domain name system (Namecoin~\cite{namecoin}).
Further, we are interested in horizontal scalability in the general case as it enables ubiquitous use.
That is, adding more nodes to the network should result in higher transaction throughput.

### 2018-04-04 paper/s3-system.tex
Polish

\subsubsection{Bootstrap Phase}
\label{sec:bootstrap}
To bootstrap, imagine that there is some bootstrap oracle that initiates the correct program on every node,
meaning that it satisfied the properties in \Cref{def:consensus}.
In practice, the bootstrap oracle is most likely the software developer that sets up the system and assigns the facilitators of round 1.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

@@

There are two scenarios in the consensus phase.
First, if $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h-1} \rangle$ to all the facilitators.
Second, if $u$ is a facilitator, it waits until $N - t$ messages of type \texttt{cp\_msg} are received.
% Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
Invalid messages are removed.
Those are blocks with invalid signatures and blocks signed by the same key.
With the sufficient number of \texttt{cp\_msg} messages,
it begins the ACS algorithm and some $\C'_{r + 1}$ should be agreed upon by the end of it.
Duplicates and blocks with invalid signatures are again removed from $\C'_{r+1}$ and we call the final result $\C_{r+1}$.
We have to remove invalid blocks a second time because the adversary may send different CP blocks to different facilitators,
which results in invalid blocks in the ACS output, but not in any of the inputs.

The core of the consensus phase is the ACS algorithm,
which is derived from HoneyBadgerBFT~\cite{miller2016honey}.
We do not use the full HoneyBadgerBFT due to the following.
First, the transactions in HoneyBadgerBFT are first queued in a buffer and the main consensus algorithm starts only when the buffer reaches an optimal size.
We do not have an infinite stream of CP blocks, thus buffering is unsuitable.
Second, HoneyBadgerBFT uses threshold encryption to hide the content of the transactions.
But we do not reach consensus on transactions, only CP blocks;
the content of the CP blocks are not sensitive so there is no need to hide it.

Continuing, when $\F_{r}$ finish the ACS execution and reach agreement on $\C_{r+1}$,
they immediately broadcast two messages to all the nodes---first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
The channels are not authenticated, 
and there are no signatures in $\C_{r + 1}$.
If a non-facilitator sees some $\C_{r + 1}$, it cannot immediately trust it because it may have been forged.
Thus, to guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

@@

Up to this point, we do not provide a mechanism to detect tampering.
The validation protocol $\Pi_v$ aims to solve this issue.
The protocol is also a request-response protocol.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

@@

\subsection{Fair Facilitator Election}
Our consensus protocol does not guarantee fair facilitator election when dedicated attackers are present.
If a malicious facilitator is elected, it can delay, eavesdrop and collect all CP block messages before sending its own.
Effectively, it can predict the consensus result before the facilitators start the consensus protocol, and generate a CP block such that the malicious node has an unfair advantage of being elected as a facilitator in the next round.

>>>>

\subsubsection{Bootstrap Phase}
\label{sec:bootstrap}
To bootstrap, imagine that there is some bootstrap oracle that initiates the correct program on every node,
meaning that it satisfied the properties in \Cref{def:consensus}.
In practice, the bootstrap oracle is most likely a group of software developers
(representing different organisations)
that agreed to work together to set up the system and assign the facilitators of round 1.
The number of facilitators is $n$, we discuss the trade-offs for different values of $n$ in~\Cref{sec:implementation}.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

@@

There are two scenarios in the consensus phase.
First, if $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h-1} \rangle$ to all the facilitators.
Second, if $u$ is a facilitator, it waits for $N - t$ messages of type \texttt{cp\_msg}.
% Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
Invalid messages are removed,
which are blocks with invalid signatures and blocks signed by the same key.
With a sufficient number of \texttt{cp\_msg} messages,
it begins the ACS algorithm and some $\C'_{r + 1}$ should be agreed upon by the end of it.
Duplicates and blocks with invalid signatures are again removed from $\C'_{r+1}$ and we call the final result $\C_{r+1}$.
We have to remove invalid blocks a second time because the adversary may send different CP blocks to different facilitators,
which results in invalid blocks in the ACS output, but not in any of the inputs.

The core of the consensus phase is the ACS algorithm,
which is described in HoneyBadgerBFT~\cite{miller2016honey}.
We do not use the full HoneyBadgerBFT due to the following.
First, the transactions in HoneyBadgerBFT are first queued in a buffer and the main consensus algorithm starts only when the buffer reaches an optimal size.
We do not have an infinite stream of CP blocks, thus buffering is unsuitable.
Second, HoneyBadgerBFT uses threshold encryption to hide the content of the transactions.
But we do not reach consensus on transactions, only CP blocks;
the content of the CP blocks are not sensitive so there is no need to hide it.

When $\F_{r}$ finish the ACS execution and reach agreement on $\C_{r+1}$,
they immediately broadcast two messages to all the nodes---first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
The channels are not authenticated, 
and there are no signatures in $\C_{r + 1}$.
If a non-facilitator sees some $\C_{r + 1}$, it cannot immediately trust it because it may have been forged.
Thus, to guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

@@

Up to this point, we do not provide a mechanism to detect tampering.
The validation protocol $\Pi_v$ aims to solve this issue.
The protocol is also a request-response protocol.
Before explaining the protocol itself, we first define what it means for a transaction to be valid.

@@

\subsection{Unbiased Facilitator Election}
Our consensus protocol does not guarantee unbiased facilitator election when dedicated attackers are present.
If a malicious facilitator is elected, it can delay, eavesdrop and collect all CP block messages before sending its own.
Effectively, it can generate a CP block such that it has an unfair advantage of being elected as a facilitator in the next round.

### 2018-04-04 paper/s5-evaluation.tex
Edit paper before defence
Polish

@@

A free and open source implementation can be found on GitHub: \url{https://github.com/kc1212/checo}.
It implements the three protocols and the Extended TrustChain.
We also implement the caching optimisation discussed in \Cref{sec:caching}.
It is written in the Python programming language.
The cryptography primitives we use are SHA256 for hash functions and Ed25519 for digital signatures.

@@

The downside of our design is that the communication complexity of the consensus protocol grows polynomially as the number of facilitators grows linearly.
Hence, the consensus protocol will take longer to complete, and larger fragments must be sent for transaction verification.
On the other hand, it does not significantly impact the throughput;
only the transaction verification delay is affected.
We refer the reader to~\cite[Chapter 5]{checo} for additional analysis of the effect of the number of facilitators as well as other experimental results.

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{neighbour-random/round-duration-vs-facilitators}
    \caption{The consensus duration increases polynomially with respect to the number of facilitators.}
    \label{fig:round-duration-vs-facilitators}
\end{figure}

@@

A free and open source implementation can be found on GitHub: \url{https://github.com/kc1212/checo}.
It implements the three protocols and the Extended TrustChain.
We also implement the caching optimisation discussed in \Cref{sec:caching}.
The cryptography primitives we use are SHA256 for hash functions and Ed25519 for digital signatures.

@@

The downside of our design is that the communication complexity of the consensus protocol grows polynomially with respect to the number of facilitators.
Hence, the consensus protocol will take longer to complete, and larger fragments must be sent for transaction verification.
On the other hand, it does not significantly impact the throughput;
only the transaction verification delay is affected.
The experimental results in \Cref{fig:round-duration-vs-facilitators} demonstrates this issue, it uses the same experimental-setup as before.
We refer the reader to~\cite[Chapter 5]{checo} for additional analysis of the effect of the number of facilitators as well as other experimental results.
